Parallel Multi-objective Optimization on CPU Using Information Framework for Constructing Global Optimization Algorithms

### 2017-07-12 2017/URAL-PDC/u_pdc_paper.tex
u_pdc: small fix in intro section

To find the complete set of efficient or weakly efficient points is the most computationally
complex problem, however it provides a wide choice of possible compromised solutions. A
plenty of approaches to the finding of these sets has been developed: the application of the
genetic algorithms to the multi-objective problem directly~\cite{DebPratap2002}, the use of the
parametric convolutions reducing the problem to a series of the scalar global optimization
problems~\cite{GergelKozinov2017}, various approaches to the solving the problems with the
convex~\cite{ZhangZuo2013} or linear~\cite{Benson1998} objectives. The main problem in the
using of majority of these methods is the absence of the theoretical guarantee of the uniform
convergence to the whole sought set of the Pareto-optimal solutions on a wide class of
problems including the ones with the non-convex multiextremal criteria. A method having this
property in the case, when all criteria satisfy the Lipschitz condition has been developed on the
basis of the information global search algorithm~\cite{markinStrongin1993}. In the present
paper, the parallel and accelerated by the local refinement technique~\cite{strOptBook}(chapter
3) modification of this method will be considered.

>>>>

To find the complete set of efficient or weakly efficient points is the most computationally
complex problem, however it provides a wide choice of possible compromised solutions. A
plenty of approaches to the finding of these sets has been developed: the application of the
genetic algorithms to the multi-objective problem directly~\cite{DebPratap2002}, the use of the
parametric convolutions reducing the problem to a series of the scalar global optimization
problems~\cite{GergelKozinov2017}, various approaches to the solving the problems with the
convex~\cite{ZhangZuo2013} or linear~\cite{Benson1998} objectives. The main problem in the
using of the most of these methods is the absence of the theoretical guarantee of the uniform
convergence to the whole sought set of the Pareto-optimal solutions on a wide class of
problems including the ones with the non-convex multiextremal criteria. A method having this
property in the case, when all criteria satisfy the Lipschitz condition has been developed on the
basis of the information global search algorithm~\cite{markinStrongin1993}. In the present
paper, the parallel and accelerated by the local refinement technique~\cite{strOptBook}(chapter
3) modification of this method will be considered.
